

\begin{flushleft}
	
	\begin{itemize}
		\item \textbf{main()} is entry point for a Java program. 
		\item JVM looks for main() in the class \& executes it.
		\item JVM searches for main() with below prototype:
		\bigskip
		\syntaxblock{
			public static void main(String[] args)
		}
	
		\begin{itemize}
			\item \textbf{public:} Modifier to call main() from anywhere
			\item \textbf{static:} without any object, JVM can call this method
			\item \textbf{void:} Return nothing to JVM
			\item \textbf{main:} Method name JVM calls by default
			\item \textbf{String[] args:} command line argument
		\end{itemize}
		\bigskip
		\noteblock{
			\begin{itemize}
				\item main() syntax is strict \& any change in this will result in runtime error: "NoSuchMethodError: main".
				\item Compiler does not check Whether class contains main() or not.
				\item JVM is responsible to check main.
				\item JVM will throw runtime exception if main() is not declared correctly.
			\end{itemize}
			}
		\item Changes allowed in main():
		\begin{itemize}
			\item Order of modifier can be changed:
			\newline
			Eg: \textbf{static public void main(String[] args)}
			\item The command line argument’s string array identifier can change:
			\newline
			Eg: \textbf{public static void main(String temp[])}
			\item String array can be taken as var\_arg parameter
			\newline
			Eg: \textbf{public static void main(String… args)}
			\item main() method can be declared with following modifiers:
			\begin{itemize}
				\item final
				\item synchroised
				\item strictfop
			\end{itemize}
			Eg:
			\codeblockfull{New.java}{
				class New \{ \\
				\s static final synchronized strictfp public void main(String... name)\{ \\
				\s \s System.out.println("Valid main method"); \\
				\s \} \\
				\} 
			}
		\end{itemize}
		\bigskip
		\item Multiple main() methods i.e method over-loading is possible!. However JVm will always call String[] argument main method only.
		\bigskip
		\codeblockfull{New.java}{
			class New \{ \\
			\s	public static void main(String[] args)\{ \\
			\s	\s	System.out.println("Starting");  // Output: Starting \\
			\s	\} \\
			\s	public static void main(int[] args)\{ \\
			\s \s		System.out.println("Sample 2"); \\
			\s	\} \}
		}

	\end{itemize}
	
\end{flushleft}
\newpage



