\setlength{\columnsep}{3pt}
\begin{flushleft}

	\tabletwo{
	\hline
	Interface & Abstract Class \\
	\hline
	Used when you dont know anything about implementation, you just have requirement specification &
	Used when you know about partial implementation \\
	\hline	
	Every method is always public and abstract whether we are declaring or not. It is 100\% abstract class & 
	Methods need not be public and abstract. Methods can be concrete \\
	\hline
	You can't declare with the following modifiers 
	\begin{itemize}
		\item Private
		\item Protected
		\item Static
		\item Final
		\item Native
		\item Syncronised
		\item Strictfp		
	\end{itemize} &
	There are no restrictions on abstract class method modifiers. \\
	\hline	
	Variable is always “public static final” whether we are declaring it or not & 
	Variable present inside abstract class need not be public static final.  \\
	\hline
	
	Variables should perform initialization at the time of declaration & 
	Variables are not required to perform initialsation at the time of declaration \\
	\hline
	
	Interface can’t declare static and instance blocks & Can contain static and instance blocks
	\\
	
	\hline
	
	Cannot contain constructors & Can declare constructors \\
	\hline
	}	

	\newpage
	
	\quest{Why abstract class can contain constructor but interface does not contain constructor?}
	{
	\begin{itemize}
		\item The main purpose of constructor is to perform initialisation for the instance variables.
		\item Abstract class can contain instance variables, (for child object to perform initialsation of those instance variable) hence constructor is required for abstract.
		\item But, every variable present inside interface is always \textbf{public static final} whether you are declaring or not.
		\item Also there are no instance variables inside interface, hence constructor concept is not required for interface.		
	\end{itemize}
	}
	\bigskip
	\quest{Inside interface, every method is always abstract and abstract class also contains abstract methods. Is it possible to replace interface with abstract class?
	}{
	\begin{itemize}
		\item You can replace interface with abstract class, but it is not a good programming practise.
		\item If everything is abstract, then it is highly recommended to go interface \& not abstract class.
	\end{itemize}
	}

\end{flushleft}
\newpage

