\begin{flushleft}
	
	\begin{itemize}
		\item RDBMS is a type of DBMS that stores and manages data in tables. 
		\item It is designed using relational model.
	\end{itemize}

	\textbf{Relational Model}: It is a framework introduced by E.F. Codd in 1970. It organize and manage data within DBMS as follows:
	\begin{itemize}
		\item \textbf{Tables:} 
		\begin{itemize}
			\item Tables are relations.
			\item Table contains rows (records) and columns (attributes or fields).
			\item Each row is unique record.
			\item Each column is attribute.
		\end{itemize}
		
		\item \textbf{Tables have a Primary Key:}
		\begin{itemize}
			\item A primary key is a column (or set of columns) that uniquely identifies each table record. 
			\item Primary key ensures records are not duplicate.
		\end{itemize}
	
		\item \textbf{Foreign Key:}
		\begin{itemize}
			\item Table relations are established using foreign keys. 
			\item A foreign key in one table refers to the primary key in another table.
		\end{itemize}
	
		\item \textbf{Data Integrity:}
		\begin{itemize}
			\item Defines constraints, such as uniqueness, null values, ensures foreign keys reference valid primary keys etc.
		\end{itemize}
	
		\item \textbf{Structured Query Language (SQL):}
		\begin{itemize}
			\item Use SQL (Structured Query Language) for querying and manipulating data. 
			\item SQL allows users to perform operations like SELECT, INSERT, UPDATE, DELETE etc.
		\end{itemize}
	
		\item \textbf{Data Independence:}
		\begin{itemize}
			\item The relational model promotes a separation between physical storage and logical representation of data. 
			\item Changes to the physical storage do not affect data being accessed or queried.
		\end{itemize}
	
		\item \textbf{Normalization:}
		\begin{itemize}
			\item Organize the database tables to minimize redundancy and anomalies.
		\end{itemize}
	
		\item \textbf{Adherence to Codd's Rules:}
		\begin{itemize}
			\item Codd formulated 12 rules  that makes a system fully compliant with relational model.
		\end{itemize}
	
		\item \textbf{ACID Transactions}: RDBMS supports ACID (Atomicity, Consistency, Isolation, Durability) properties.
	\end{itemize}
	
\end{flushleft}
